A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
Modified related work.

\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Conclusion}
\label{sec:conclusion}
In this project, we presented a framework of a digital library for transient crowds in highly-dynamic social messaging systems like Twitter and Facebook. We built a framework that allows an analyst or curious user to find interesting crowds and see how they evolve.  The framework enabled clients to interact with the library using JSON APIs. The APIs enabled searching and browsing of the digital library.
